Adaptive global optimization using graphics accelerators\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-05-27 2020/RSD_GPU/RSD2020.tex
Исправлена ошибка в таблице с шестимерными задачами.
Add calculation time

Note that well-known test problems from the field of multidimensional global optimization are characterized by a short time of calculating the values of the objective function. Therefore, in order to simulate the computational complexity inherent in applied optimization problems \cite{Modorskii2016}, the calculation of the objective function in all experiments was complicated by additional calculations that do not change the form of the function and the location of its minima (summing the segment of the Taylor series).

@@

\begin{table}
                \caption{Speedup on six GPUs}
                \label{table:GKLS6_average_MMAS_GPU}
                \center
                \begin{tabular}{lccc}
                               %\hline\noalign{\smallskip}
                &  Iteration speedup & &   Time speedup \\
                               \noalign{\smallskip} \hline \noalign{\smallskip}                               
                               $p=64$  &    11,3	 & & 6,8	  \\
                               $p=256$ &    39,0	 & & 31,5  \\
															 $p=1024$&    128,4	 & & 83,5  \\
                               \noalign{\smallskip}\hline
                \end{tabular}
\end{table}

@@

The last series of experiments has been carried out on 100 six-dimensional problems from the GKLS Simple class. 
Table \ref{table:GKLS6_average_MMAS_GPU} shows the speedup of the algorithm combining multiple evolvents and the adaptive scheme when solving the problems on 3 cluster nodes (using 2 GPUs per node, 6144 GPU threads in all) compared to the adaptive scheme on CPU using 4 threads.

>>>>

Note that well-known test problems from the field of multidimensional global optimization are characterized by a short time of calculating the values of the objective function. Therefore, in order to simulate the computational complexity inherent in applied optimization problems \cite{Modorskii2016}, the calculation of the objective function in all experiments was complicated by additional calculations that do not change the form of the function and the location of its minima (summing the segment of the Taylor series). 
In the experiments carried out the average time for calculating the function values was 0.01 seconds.

@@

\begin{table}
                \caption{Speedup on six GPUs}
                \label{table:GKLS6_average_MMAS_GPU}
                \center
                \begin{tabular}{lccc}
                               %\hline\noalign{\smallskip}
                &  Iteration speedup & &   Time speedup \\
                               \noalign{\smallskip} \hline \noalign{\smallskip}                               
                               $p=64$  &    30,8	 & & 1,9	  \\
                               $p=256$ &    92,7	 & & 1,5  \\
							   $p=1024$&    597,0	 & & 2,5  \\
                               \noalign{\smallskip}\hline
                \end{tabular}
\end{table}

@@

The last series of experiments has been carried out on 20 six-dimensional problems from the GKLS Simple class. 
Table \ref{table:GKLS6_average_MMAS_GPU} shows the speedup of the algorithm combining multiple evolvents and the adaptive scheme when solving the problems on 3 cluster nodes (using 2 GPUs per node, 6144 GPU threads in all) compared to the adaptive scheme on CPU using 4 threads.
